---
title: "Data Viz 3"
description: |
   Relationship between parent report of executive function and children's perfomance.
author:
  - name: Karlena Ochoa
    url: https://example.com/norajones
date: 03-10-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load libraries }

library(tidyverse)
library(janitor)
library(rio)
library(magrittr)
library(here)
library(knitr)
library(stats)
library(gghighlight)
library(showtext)
library(ggthemes)
library(grid)
library(gganimate)
library(ungeviz)
library(gifski)
library(colorblindr)
library(distill)

```


```{r import data}

df <- import(here("data", "BREIF_Data_100p_final_proj.csv"),
             na.string = "999")
             
df2 <- import(here("data", "data_trust_final_proj.csv"),
              na.string = "999")

# turn 999 into nas

#join data and select variables of interest 

data <- left_join(df2, df, by = "subid") %>% 
  select(1, 4:7, 12:23, 25:28, 33:44, 56:73, 81:143)
  
```

# Visualization 1: Aimed at the scientific community!

message: present parents' report of children's executive function (EF) performance and children's actually prefermonace on EF tasks by age. 

```{r viz 3}

#make data into long format
df4 <- data %>%
  gather(BRIEF_item, BRIEF_response, "BRIEF1":"BRIEF63") %>%
  mutate(BRIEF_item = as.factor(parse_number(BRIEF_item))) %>%
  mutate(BRIEF_response = as.numeric(BRIEF_response)) %>% 
  group_by(subid) %>%  
  mutate(child_EF = ((flanker_rs + dccs_rs)/2)) %>% 
  mutate(parent_EF = sum(BRIEF_response)) %>% 
  filter(!is.na(parent_EF)) %>% 
  filter(!is.na(child_EF)) %>% 
  mutate(parent_EF_RS = (63 - parent_EF)) %>% 
  mutate(agegroup.x = recode(agegroup.x,
                              "3" = "3-year-olds",
                              "4" = "4-year-olds")) 
```

Examine variables of interest for outliers 

Child EF
```{r}
boxplot(df4$child_EF)
```

Parent report of child EF 

```{r}
boxplot(df4$parent_EF_RS)
```

Parent report EF and child EF

```{r}
ggplot(df4, aes(child_EF, parent_EF_RS, group = agegroup.x)) + 
  geom_boxplot()
```

# This is the first version of the visualization.

My plan was to highlight the outliers in the plot, but there were no outliers. I added titles and axes labels and increased size of labels. I decided to add a regression line and try out a new theme. 

```{r}
plot <- ggplot(df4, aes(child_EF, parent_EF_RS)) +
  geom_point(size = 1.5, color = "gray40") +
  geom_smooth(method = "lm") +
  theme_bw() + 
  labs(title= "Children's Executive Function Score in \nRelation to Parent Report of Executive Function",
       x = "Children's Executive Function Score",
       y = "Parent-Report of Executive Function" )

plot + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=15),
           plot.subtitle = element_text(size=14),
           strip.text.x = element_text(size = 12))
```

## This is the final plot for the scientific community. 

I decided to facet the plot by age group rather than color by age like in my first visualization. I decided to keep the SE on the regression line because I believe it shows that there is more uncertainty for 3-year-olds. 

```{r}

finalviz3 <- ggplot(df4, aes(child_EF, parent_EF_RS)) +
  geom_point(size = 1.5, color = "gray40") +
  geom_smooth(method = "lm") +
  facet_wrap(~agegroup.x) +
  theme_bw() + 
  labs(title= "Children's Executive Function Score in Relation to Parent Report of Executive Function",
       subtitle = "Relationship separated by age", 
       x = "Children's Executive Function Score",
       y = "Parent-Report of Executive Function" )

finalviz3 + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=15),
           plot.subtitle = element_text(size=14),
           strip.text.x = element_text(size = 12))
```
