---
title: "Data Viz 2"
description: |
  Children's performance in the trust task when they received first-hand information.
author:
  - name: Karlena Ochoa 
    url: https://example.com/norajones
date: 03-12-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load libraries }

library(tidyverse)
library(janitor)
library(rio)
library(magrittr)
library(here)
library(knitr)
library(stats)
library(gghighlight)
library(showtext)
library(ggthemes)
library(grid)
library(gganimate)
library(ungeviz)
library(gifski)
library(colorblindr)
library(distill)

```


```{r import data}

df <- import(here("data", "BREIF_Data_100p_final_proj.csv"),
             na.string = "999")
             
df2 <- import(here("data", "data_trust_final_proj.csv"),
              na.string = "999")

# turn 999 into nas

#join data and select variables of interest 

data <- left_join(df2, df, by = "subid") %>% 
  select(1, 4:7, 12:23, 25:28, 33:44, 56:73, 81:143)
  
```

# Visualization 2: Aimed at the scientific community!

Message: overall there is a positive relationship between children that received first-hand information regarding informants' traits and their performance on the training trials and trust of more reliable informant.

## This is the first version of the visualization. 

Clearly there is a lot of work to be done. 

```{r viz 2, fig.width = 5, fig.height = 6}
df3 <- df2 %>% 
  filter(condition == "1") 

#Let's make this sad scatter plot better

ggplot(df3, aes(trainingtotal, total_trust)) +
  geom_point()

```

## This is the second version of the visualization. 

For this version I added theme minimal and added jitter for overlapping points. I also decided to add a regression line with SE to model the relationship. 

```{r plot 6}
#theme minimal added jitter for overlapping points 
plot6 <- ggplot(df3, aes(trainingtotal, total_trust)) +
  geom_point(position = "jitter") +
  geom_smooth(method = "lm", fullrange = TRUE) +
  theme_minimal() +
  labs(title= "Children's Performance on Training Trials Related \nto Total Trust of Reliable Informant", 
       subtitle = "", 
       x = "Training Total", y = "Trust Score" )
plot6
```

## This is the third version of the visualization. 

For this plot I thought it would be helpful to separate the regression lines by age since there is an age difference in trust scores. 

```{r plot 6.1}

#color dots and regression line by age group 
ggplot(df3, aes(trainingtotal, total_trust, colour = as.factor(agegroup.x))) +
  geom_point() +
  geom_jitter(position = position_jitter(height = .6, width = 0)) +
  geom_smooth(method = "lm", fullrange = TRUE, se = FALSE) +
  scale_fill_brewer(palette = "Accent",
                     name = "Age Group",
                     breaks = c("3", "4"),
                     labels = c("3-year-olds", "4-year-olds")) +
  scale_color_OkabeIto() +
  theme_minimal() +
  labs(title= "Children's Performance on Training Trials Related to Total \nTrust of Reliable Informant", 
       subtitle = "Relationship separated by age", 
       x = "Training Total",
       y = "Trust Score" )

```


## This is the final version of the visualization. 

For the final version of the plot I decided to try and reduce the cognitive load by annotating regression lines rather than using a legend. 


```{r final plot}

#add annotations and remove legend. Decided to remove subtitle, not needed (too much text) 

finalviz2 <- ggplot(df3, aes(trainingtotal, total_trust, colour = as.factor(agegroup.x))) +
  geom_point() +
  geom_jitter(position = position_jitter(height = .6, width = 0)) +
  geom_smooth(method = "lm", fullrange = TRUE, se = FALSE) +
  scale_fill_brewer(palette = "Accent",
                     name = "Age Group",
                     breaks = c("3", "4"),
                     labels = c("3-year-olds", "4-year-olds")) +
  scale_color_OkabeIto() +
  theme_minimal() +
  labs(title= "Children's Performance on Training Trials \nRelated to Total Trust of Reliable Informant", 
       x = "Training Total",
       y = "Trust Score" ) +
  annotate("text", label = "3-year-olds", x = 2.8, y = 3.0, size = 4.5) +
  annotate("text", label = "4-year-olds", x = 2.8, y = 5.0, size = 4.5) +
  guides(color = "none")


finalviz2 + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=15),
           plot.subtitle = element_text(size=14))

```

