---
title: "Data Viz 1"
description: |
  Examines young children's trust of reliable informant.
author:
  - name: Karlena Ochoa 
    url: https://example.com/norajones
date: 03-13-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(janitor)
library(rio)
library(magrittr)
library(here)
library(knitr)
library(stats)
library(gghighlight)
library(showtext)
library(ggthemes)
library(grid)
library(gganimate)
library(ungeviz)
library(gifski)
library(colorblindr)
library(distill)
```

```{r import data}

df <- import(here("data", "BREIF_Data_100p_final_proj.csv"),
             na.string = "999")
             
df2 <- import(here("data", "data_trust_final_proj.csv"),
              na.string = "999")

# turn 999 into nas

#join data and select variables of interest 

data <- left_join(df2, df, by = "subid") %>% 
  select(1, 4:7, 12:23, 25:28, 33:44, 56:73, 81:143)
  
```
# Visualization 1: Aimed at the general community!

Message: only 4-year-olds trust the reliable informant over the unreliable informant, even when 3-year-olds receive first-hand information they are equally choosing the reliable (helpful) and unreliable informant (tricky) in a sticker-finding task. 

## This is the first version of the visualization. 

```{r viz 1}
#mutate variables to factors and label, make average trust variable
v1 <- data %>% 
mutate(condition = as.factor(ifelse(condition == 1, "first-hand",     
                                      "second-hand"))) %>%
  mutate(gender = as.factor(ifelse(gender == 1, "male", "female"))) %>%
  group_by(subid) %>%
  mutate(average_trust = mean(total_trust))

summary_p <- v1 %>%
  group_by(agegroup.x, condition) %>%
  summarise(n = n(),
            average_trust = mean(total_trust),
            sd_average_trust = sd(total_trust),
            se_average_trust = sd_average_trust / (sqrt(n)))

plot1 <- ggplot(summary_p, aes(as.factor(agegroup.x), average_trust)) +
  geom_bar(aes(fill = condition), stat = "identity", position = "dodge",
           alpha = .7) +
    labs(title= "Children's Selective Trust of Helpful over Tricky informant", 
       subtitle = "Separated by Condition and Age group", 
       x = "Age Group", y = "Average Trust Score" ) +
     geom_errorbar(aes(ymin = average_trust - 1.96*se_average_trust, 
                       ymax = average_trust + 1.96*se_average_trust,
                       group = condition),
                  width=.2,                    
                  position = position_dodge(width = 0.9)) +
  theme_minimal() 

plot1

```

## This is the second version of the visualization.

For this version I changed the colors and increased font size for labels and axes. 

```{r viz 2}
plot2 <- ggplot(summary_p, aes(as.factor(agegroup.x), average_trust)) +
  geom_bar(aes(fill = condition), stat = "identity", position = "dodge",
           alpha = .6) +
  ylim(c(0,6)) +
    labs(title= "Children's Selective Trust of Helpful over Tricky informant", 
       subtitle = "Separated by Condition and Age group", 
       x = "Age Group", y = "Average Trust Score" ) +
     geom_errorbar(aes(ymin = average_trust - 1.96*se_average_trust, 
                       ymax = average_trust + 1.96*se_average_trust,
                       group = condition),
                  width=.2,                    
                  position = position_dodge(width = 0.9)) +
  theme_classic() +
  scale_fill_OkabeIto()


plot2 + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=16),
           plot.subtitle = element_text(size=14))

```

## This is the third version of the visualization.

For this version I tried adding annotations of the mean and tried out a different color. It's too much. 

```{r viz 3}
plot3 <- ggplot(summary_p, aes(as.factor(agegroup.x), average_trust )) +
  geom_bar(aes(fill = condition), stat = "identity", position = "dodge",
           alpha = .5) +
  ylim(c(0,6)) +
    labs(title= "Only 4-year-olds trust the more reliable informant!", 
       subtitle = "", 
       x = "Age Group", y = "Average Trust Score" ) +
     geom_errorbar(aes(ymin = average_trust - 1.96*se_average_trust, 
                       ymax = average_trust + 1.96*se_average_trust,
                       group = condition),
                  width=.1, 
                  alpha = .5,
                  color = "gray40",
                  position = position_dodge(width = 0.9)) +
  annotate("text", label = "3.43", x = .79, y = 3.43, fontface = "bold", size = 4) +
  annotate("text", label = "3.32", x = 1.2, y = 3.32, fontface = "bold", size = 4) +
  annotate("text", label = "4.71", x = 1.8, y = 4.71, fontface = "bold", size = 4) +
  annotate("text", label = "3.96", x = 2.2, y = 3.96, fontface = "bold", size = 4) +
  theme_classic() +
  scale_fill_viridis_d(option = "cividis")


plot3 + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=16),
           plot.subtitle = element_text(size=14))
```

## This is the final version of theplot for the general community.

For this one I decided to remove the error bars and keep the OkabeIto colors. 

```{r viz 4}
plot4 <- ggplot(summary_p, aes(as.factor(agegroup.x), average_trust )) +
  geom_bar(aes(fill = condition), stat = "identity", position = "dodge",
           alpha = .5) +
  ylim(c(0,6)) +
    labs(title= "Only 4-year-olds trust the more reliable informant!", 
       subtitle = "Children's selective trust in a sticker-finding game", 
       x = "Age Group", y = "Average Trust Score" ) +
  annotate("text", label = "3.43", x = .79, y = 3.61, size = 5) +
  annotate("text", label = "3.32", x = 1.2, y = 3.5, size = 5) +
  annotate("text", label = "4.71", x = 1.8, y = 4.9, size = 5) +
  annotate("text", label = "3.96", x = 2.2, y = 4.2, size = 5) +
  theme_classic() +
  scale_fill_OkabeIto()

plot4 + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=18),
           plot.subtitle = element_text(size=14)) +
    guides(fill = guide_legend(title = "Condition"))

v1 <- v1 %>% 
  mutate(condition = recode(condition,
                "first-hand" = "First-hand",
                "second-hand" = "Second-hand")) 

```

## This is the first version for scientific community.

I thought the above plot would be good for the general public but I wanted to see the individual points to show uncertainty. I don't think this plot would be good for the general community so I made a rendition for the scientific community. 

```{r viz 5}
plot5 <- ggplot(v1, aes(as.factor(agegroup.x), total_trust, color = (as.factor(agegroup.x)))) +
  geom_point(alpha = 0.9, position = position_jitter(height = .2, width = .2)) +
  facet_wrap(~condition) +
  theme_minimal() +
  scale_color_brewer(palette = "Accent") +
    labs(title= "Only 4-year-olds trust the more reliable informant!", 
       subtitle = "Children's trust scores in a sticker-finding game", 
       x = "Age Group",
       y = "Trust Score of Reliable Informant")

plot5 +
  theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=15),
           plot.subtitle = element_text(size=14),
           strip.text.x = element_text(size = 12),
           legend.position = "none") 
```

## This is the final plot for the scientific community. 

I decided the pastel colors were too light and wanted to show the mean line for the group with the individual points. 

```{r viz for scientific community}
v2 <- v1 %>%  group_by(agegroup.x, condition) %>%
       summarise(n = n(),
            average_trust = mean(total_trust))


finalviz1 <- ggplot(v1, aes(as.factor(agegroup.x), total_trust, color = (as.factor(agegroup.x)))) +
  geom_point(alpha = 0.9, position = position_jitter(height = .2, width = .2)) +
  facet_wrap(~condition) +
  theme_minimal() +
  scale_color_OkabeIto() +
    labs(title = "Only 4-year-olds trust the more reliable informant!", 
       subtitle = "Children's trust scores in a sticker-finding game", 
       x = "Age Group",
       y = "Trust Score",
       caption = "\nBlack bars represent mean trust score per group.") +
  stat_summary(aes(colour = average_trust), geom = "hpline", width = 0.3, size = .6)


finalviz1 + 
  theme(axis.title.x = element_text(size = 14),
           axis.text.x = element_text(size = 12),
           axis.title.y = element_text(size = 14),
           axis.text.y= element_text(size = 12),
           plot.title = element_text(size = 15),
           plot.subtitle = element_text(size = 14),
           strip.text.x = element_text(size = 12),
           legend.position = "none")

```


