---
title: "Data Viz 4"
description: |
  Trust of reliable informant across age.
author:
  - name: Karlena Ochoa
    url: https://example.com/norajones
date: 03-11-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load libraries }

library(tidyverse)
library(janitor)
library(rio)
library(magrittr)
library(here)
library(knitr)
library(stats)
library(gghighlight)
library(showtext)
library(ggthemes)
library(grid)
library(gganimate)
library(ungeviz)
library(gifski)
library(colorblindr)
library(distill)
library(transformr)

```


```{r import data}

df <- import(here("data", "BREIF_Data_100p_final_proj.csv"),
             na.string = "999")
             
df2 <- import(here("data", "data_trust_final_proj.csv"),
              na.string = "999")

# turn 999 into nas

#join data and select variables of interest 

data <- left_join(df2, df, by = "subid") %>% 
  select(1, 4:7, 12:23, 25:28, 33:44, 56:73, 81:143)
  
```

# Visualization 4: Aimed at the scientific community!

message: children's ability to trust a reliable informant over an unreliable informant increases with age. 

## This is the first version of the visualization. 

```{r}
df5 <- df2 %>% 
mutate(gender = recode(gender,
                "0" = "Girls",
                "1" = "Boys"))


plot7.v1 <- ggplot(df5, aes(exactage.x, total_trust)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm") +
  theme_bw() + 
  labs(title = "Children's Age in Relation to Trust of the Reliable Informant",
       x = "Age in Months",
       y = "Total Trust Score") 

plot7.v1 + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=15),
           plot.subtitle = element_text(size=14),
           strip.text.x = element_text(size = 12),
           panel.spacing.x = unit(1.5, "cm"))

```

## This is the second version of the visualization. 

I decided to facet by gender because sometimes there are gender differences in theory of mind tasks. Children's reasoning about trustworthiness requires theory of mind. I also increased the space between the panels for readability. I also decided to add color for gender and remove the legend. 

```{r}

plot7 <- ggplot(df5, aes(exactage.x, total_trust, color = gender)) +
  geom_point(alpha = 0.6) +
  facet_wrap(~gender) +
  geom_smooth(method = "lm") +
  theme_bw() + 
  labs(title = "Children's Age in Relation to Trust of the Reliable Informant",
       subtitle = "Separated by Gender", 
       x = "Age in Months",
       y = "Total Trust Score") +
  scale_color_OkabeIto() +
  guides(color = "none")

plot7 + theme(axis.title.x = element_text(size= 4),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=15),
           plot.subtitle = element_text(size=14),
           strip.text.x = element_text(size=12),
           panel.spacing.x = unit(1.5, "cm"))

```

## This is the final version of the visualization. 


```{r}
bsr <- bootstrapper(40, gender)

finalviz4 <- ggplot(df5, aes(exactage.x, total_trust)) +
  geom_point(alpha = 0.6) +
  geom_point(data = bsr) +
  facet_wrap(~gender) +
  geom_smooth(data = bsr, method = "lm", fullrange = TRUE) +
  theme_bw() +
  labs(title = "Children's Age in Relation to Trust of the Reliable Informant",
       subtitle = "Separated by Gender", 
       x = "Age in Months",
       y = "Total Trust Score") +
  guides(color = "none") +
  transition_states(.draw, 1, 1) + 
  enter_fade() + 
  exit_fade()

finalviz4 + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12),
           plot.title = element_text(size=15),
           plot.subtitle = element_text(size=14),
           strip.text.x = element_text(size=12),
           panel.spacing.x = unit(1.5, "cm"))

```



